Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-06-24 demystify.tex
updates

\paragraph{Acceptance Letters} Universities typically prioritize sending out acceptance letters first. This allows the admitted students to start planning and preparing for their studies. These letters go to the top candidates who are offered admission directly without being placed on a waitlist.  
Some universities have rolling admissions, meaning they send out acceptance letters as they review applications (e.g., some universities sent out letters as soon as early February). Others have a specific date when they send out the first round of acceptance letters.

\paragraph{Response Deadlines}: Accepted students are usually given a strict deadline to respond to their offers (e.g., whether they will accept the offer), often around \textbf{April 15th} in the US. This is a standard deadline for PhD programs due to the Council of Graduate Schools (CGS) Resolution. After this date, programs can gauge how many slots remain unfilled.

\paragraph{Waitlist}: If the CS program has X slots, then many strong candidates will be waitlisted. If accepted students decline the offer, then offers are sent to students on the waitlist. So if you see people getting accepted, that does not mean you are out yet.

>>>>

\paragraph{Acceptance Letters} Universities prioritize sending out acceptance letters first. This allows the admitted students to make decision and plan for their studies. These letters go to the top candidates who are offered admission directly without being placed on a waitlist.

Some universities have rolling admissions, meaning they send out acceptance letters as they review applications (e.g., some universities sent out letters as soon as early February). Others have a specific date when they send out the first round of acceptance letters.

\paragraph{Response Deadlines} Accepted students are usually given a strict deadline to make decision on their offers, often around \textbf{April 15th} in the US. This is a standard deadline for PhD programs due to the Council of Graduate Schools (CGS) Resolution. After this date, programs can gauge how many slots remain unfilled.

\paragraph{Waitlist} Most CS programs have a limited number of slots for PhD students, and thus put many students on a waitlist.  If accepted students decline the offer, then offers are sent to students on the waitlist. So if you see people getting accepted, that does not mean you are out yet.
